### 2023-01-17 README.Rmd
Updates and cleaning

`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.

You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with:

``` r
# install.packages("devtools")
devtools::install_github("iqss/clarify")
```
## Introduction

@@

The `clarify` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()`  computes average dose-response functions. `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.

@@

#Fit the model
fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married + nodegree + re74 + re75),
           data = lalonde, family = binomial)

#Simulate coefficients from a multivariate normal distribution
set.seed(123)
sim_coefs <- sim(fit)

#Apply a function that estimate the g-computation estimate for the ATT
#to models with the estimated coefficients replaced by the simulated ones
sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `log(RR)` = log(p1 / p0))
}, verbose = FALSE)

@@

#View the estimates, confidence intervals, and p-values
summary(sim_est, null = c(NA, NA, 0))

#Plot the resulting sampling distributions
plot(sim_est)
```

>>>>

`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects. See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.

## Introduction

@@

The `clarify` package was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

@@

There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions. `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.

`clarify` can be installed from CRAN using

```{r, eval = F}
install.packages("clarify")
```

You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with

```{r, eval = F}
install.packages("remotes")
remotes::install_github("iqss/clarify")
```

@@

# Fit the model
fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married
                                   + nodegree + re74 + re75),
           data = lalonde, family = binomial)

# Simulate coefficients from a multivariate normal distribution
set.seed(123)
sim_coefs <- sim(fit)

# Apply a function that computes the g-computation estimate for the ATT
# to models with the estimated coefficients replaced by the simulated ones
sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `log(RR)` = log(p1 / p0))
}, verbose = FALSE)

@@

# View the estimates, confidence intervals, and p-values
summary(sim_est, null = c(NA, NA, 0))

# Plot the resulting sampling distributions
plot(sim_est)
```
